Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-09-11 temp/VHzQ_pre2019/WW4C_VHzQ_20180823.tex
tex/older_tex/ removed

\iffalse
\section*{TO DOs}
{\bf For NPR: }
\begin{itemize}
\item Concentrate on reporting NIR and W1/W2 figures and tables
\item SED dust plots 
\item Check vs. Assef R90/C75 catalog.
\item Filter curve plot with LSST, Euclid and even wide JWST filters...; 
\item Check with SpIES/SHELA (but only 3.4/4.6$\mu$m; 
\item Almost certainly want to compile M$_{\rm BH}$; THIS CAN WAIT, otherwise is massive paper-creep
\item May well wanna try and get M$_{\star}$ too...!! (yuck); THIS CAN WAIT, otherwise is massive paper-creep
\end{itemize}

@@

\section{Data}
We assemble our dataset in a relatively straightforwad manner.  First
we compile the list of all known, spectroscopically confirmed quasars
from the literature. Most of these objects are easily identified by
their broad Ly$\alpha$ emission line, \nv emission and characteristic
shape blueward of 1215\AA\ observed. As we shall see, some of the more
recently discovered objects are close to the galaxy luminosity
function characteristic luminosity $M^{*}$, and some have relatively
weak or maybe even completely absorbed Ly$\alpha$ \citep[e.g. Figures
7 and 10 in][]{Banados2016}. We leave aside detailed investigation and
discussion into espectral features and line strengths, and take as given 
the published spectra.

@@

@@

\subsection{Very high redshift quasars}
In Table~\ref{tab:THE_TABLE} we present our dataset. 
We have obtained a list of 424 spectroscopically confirmed 
quasars with redshifts $z\geq5.00$.

@@

    \subsubsection{DECam} 
    The Dark Energy Camera \citep[DECam][]{Flaugher2015} is 
    is a wide-field imager with a 2.2 degree diameter field of view 
    mounted at the prime focus of the Victor M. Blanco 4 m telescope 
    at the Cerro Tololo International Observatory. We use data 
    from both the Dark Energy Survey \citep[DES; ][]{DES2016} and 
    the DESI Legacy Imaging Survey \citep[DECaLS; ][]{Dey2018}.

%\newpage
\subsection{Near-infrared photometry}
Due to their selection of being very faint/undetected in the
observed-frame optical but bright in the observed frame near-infrared,
VH$z$Qs are generally detected in the near-infrared $yYJHK$-bands
\citep[$\approx$0.98-2.38$\mu$m; e.g., ][]{Peth2011}.

@@

\section{NIR Data}

The near-infrared data in this paper comes from the Wide Field Astronomy Unit's
(WFAU) Science Archives for UKIRT-WFCAM, the WFCAM Science Archive
\citep[WSA][]{WSA} and VISTA-VIRCAM, the VISTA Science Archive
\citep[VSA][]{VSA}. These archives were developed for the VISTA Data Flow System
\citep[VDFS][]{VDFS}.

@@

    \begin{table}
      \begin{tabular}{l r l}
        \hline  \hline
        Selection   & number detected (\%) \\
        \hline  
        Any band ($YJHK/K_{s}$   &  394  ( ) \\
        $Y$-band    &    ( ) \\
        $J$-band    &    ( ) \\
        $H$-band    &    ( ) \\
        $K$ or $Ks$-band    &    ( ) \\
        \hline  \hline
      \end{tabular}
      \caption{Detection rate of VH$z$Qs in the near-infrared.}
      \label{tab:nir_detection}
    \end{table}

@@

@@

@@

      Band & $\lambda_{\rm eff}  {\buildrel _{\circ} \over {\mathrm{A}}}$ 
              &  $\lambda_{\rm min} {\buildrel _{\circ} \over {\mathrm{A}}}$ 
              & $\lambda_{\rm max} {\buildrel _{\circ} \over {\mathrm{A}}}$ 
              & W$_{\rm eff}$ ${\buildrel _{\circ} \over {\mathrm{A}}}$ 

@@

@@

@@

@@

@@

>>>>

\iffalse
\section*{TO DOs}
{\bf For NPR: }
\begin{itemize}
\item Concentrate on reporting NIR and W1/W2 figures and tables
\item SED dust plots 
\item Filter curve plot with LSST, Euclid and even wide JWST filters...; 
\item Check for NIR and MIR variabilty with the Wu quasar
\item Check with SpIES/SHELA (but only 3.4/4.6$\mu$m; 
%%\item Almost certainly want to compile M$_{\rm BH}$; THIS CAN WAIT, otherwise is massive paper-creep
%%\item May well wanna try and get M$_{\star}$ too...!! (yuck); THIS CAN WAIT, otherwise is massive paper-creep
\end{itemize}

@@

\section{Data}
In Table~\ref{tab:THE_TABLE} we present our dataset and 
we have assembled this in the following manner.  First
we compile the list of all known, spectroscopically confirmed quasars
from the literature. Most of these objects are easily identified by
their broad Ly$\alpha$ emission line, \nv emission and characteristic
shape blueward of 1215\AA\ observed. As we shall see, some of the more
recently discovered objects are close to the galaxy luminosity
function characteristic luminosity $M^{*}$, and some have relatively
weak or maybe even completely absorbed Ly$\alpha$ \citep[e.g. Figures
7 and 10 in][]{Banados2016}. We leave aside detailed investigation and
discussion into espectral features and line strengths, and take as given 
the published spectra.

@@

Recently, Hyper Suprime-Cam \citep[HSC; ][]{Miyazaki2018} has embarked
on the Subaru Strategic Program \citep[SSP; ][]{Aihara2018a}
delivering exquisite multi-band photometry data
\citep[][]{Aihara2018b} the five broad bands $grizy$.

@@

\subsection{Spectroscopy} 
We have obtained a list of 424 spectroscopically confirmed 
quasars with redshifts $z\geq5.00$.

@@

    \iffalse
    \subsubsection{DECam} 
    The Dark Energy Camera \citep[DECam][]{Flaugher2015} is 
    is a wide-field imager with a 2.2 degree diameter field of view 
    mounted at the prime focus of the Victor M. Blanco 4 m telescope 
    at the Cerro Tololo International Observatory. We use data 
    from both the Dark Energy Survey \citep[DES; ][]{DES2016} and 
    the DESI Legacy Imaging Survey \citep[DECaLS; ][]{Dey2018}. 
    \fi

\subsection{Near-infrared photometry}
Due to their selection of being very faint/undetected in the
observed-frame optical but bright in the observed frame near-infrared,
VH$z$Qs are generally detected in the near-infrared $yYJHK$-bands
\citep[$\approx$0.98-2.38$\mu$m; e.g., ][]{Peth2011}.

@@

%\section{NIR Data}
The near-infrared data in this paper comes from the Wide Field Astronomy Unit's
(WFAU) Science Archives for UKIRT-WFCAM, the WFCAM Science Archive
\citep[WSA][]{WSA} and VISTA-VIRCAM, the VISTA Science Archive
\citep[VSA][]{VSA}. These archives were developed for the VISTA Data Flow System
\citep[VDFS][]{VDFS}.

@@

    \begin{table}
          \centering

      \begin{tabular}{l r l}
        \hline  \hline
        Selection   & number detected (\%) \\
        \hline  
        Any band ($YJHK/K_{s}$   &  394  ( ) \\
        $Y$-band    &    ( ) \\
        $J$-band    &    ( ) \\
        $H$-band    &    ( ) \\
        $K$ or $Ks$-band    &    ( ) \\
        \hline  \hline
      \end{tabular}
      \caption{Detection rate of VH$z$Qs in the near-infrared.}
      \label{tab:nir_detection}
    \end{table}

        \subsubsection{Comparing WFCAM and VISTA}
        There are 114 overlapping QSOs between WFCAM and VISTA.  Using the
        {\tt VegaToAB} value\footnote{What is this exactly??} to put these
        objects on the same AB system, and for each object compared the two
        measurements. First, the calculated weighted average (calibrated flux)
        in each filter of both and calculated the ratio and difference between
        each measurement and the average.  Then for each filter we calculated
        the weighted average of the differences (in mag) for each instrument
        to see if there were significant offsets. The results are given in
        Table~\ref{tab:WFCAM_vs_VISTA}.  The only filter with a significant
        offset is the $Y$-band. All of the VISTA averages are negative and all
        of the WFCAM ones are positive.  The $Ks$ versus $K$ band may be
        slightly dodgy, given the different shapes of the filters.
        \begin{table}
          \centering
          \begin{tabular}{l r r}
            \hline  \hline
            abs(VIRCAM & \multirow{2}{*}{millimags} &  no. of  \\
            -  WFCAM)      &                                        &  objects \\
            \hline
            $Z$                 &  19.3 	& 2 \\
            $Y$                 &  66.2 	& 48 \\
            $J$                  &    3.2 	& 105 \\
            $H$                 &  19.3     &  89 \\
            $K_{\rm s}$/$K$ &  12.7     & 93 \\
            \hline  \hline
          \end{tabular}
          \caption{Comparing the magnitudes in different WFCAM/UKIRT and VIRCAM/VISTA near-infrared bands.}
          \label{tab:WFCAM_vs_VISTA}
        \end{table}

@@

    Recently, \citet{Assef2018} released two large catalogues of AGN 
    candidates identified across 30,000 deg$^2$ of extragalactic sky 
    from the WISE AllWISE Data Release. The ``R90'' catalogue, is 
    contains 4.5M AGN candidates at 90\% reliability (and $\approx$150 
    AGN candidates per deg$^2$) while the ``C75'' catalog 
    consists of 20.9M AGN candidates at 75\% completeness (and 
    ($\approx$700 AGN candidates per deg$^2$).  Crossmatching 
    out catalogue of 424 VH$z$Qs with these catalogues, produces 
    42 matches with	the R90 sample and 98 matches with the C75 sample. 
    Both catalogues unsurprisingly match to the ultraluminous quasar 
    SDSS J0100+2802 \citep{Wu2015} while the C75, but not the R90 catalogue 
    mathes to ULAS J1120+0641 \citep{Mortlock2011}. Neither catalogue 
    matches J1342+0928 \citep{Banados2018}.

@@

All wavelengths in ${\buildrel _{\circ} \over {\mathrm{A}}}$. 

@@

      Band & $\lambda_{\rm eff}  $ 
              &  $\lambda_{\rm min} $ 
              & $\lambda_{\rm max} $ 
              & W$_{\rm eff}$

@@

       $g_{\rm HSC}$    &  	4633   &     3940     &   5546	&  1460       &    $g_{\rm HSC}$         &$  = g_{\rm AB} + 0.097 $ \\

@@

      $r_{\rm HSC}$         &    6104     &   5325    &   7071	&   1503       & $r_{\rm HSC}   $       &$     = r_{\rm AB} - 0.151 $ \\

@@

      $i_{\rm HSC}$         &   7633    &     6791    &     8658	&   1483       &  $i_{\rm PS1}    $       &$   = i_{\rm AB} - 0.396 $ \\  %% 2521.6

@@

      $z_{\rm HSC}$        &    8915  &   	8280     &      9498	&    793      & 	$Z_{\rm HSC} $         &$    = z_{\rm AB} - 0.512$     \\

@@

      $Y_{\rm HSC}$       &      9976   &    9000    & 	10931  &   1386    &  $Y_{\rm HSC}  $   &$  =Y_{\rm AB} - 0.580 $ \\

### 2019-09-11 temp/VHzQ_pre2019/WW4C_VHzQ_20180827.tex
tex/older_tex/ removed

\section{Data}
In Table~\ref{tab:THE_TABLE} we present our dataset and 
we have assembled this in the following manner.  First
we compile the list of all known, spectroscopically confirmed quasars
from the literature. Most of these objects are easily identified by
their broad Ly$\alpha$ emission line, \nv emission and characteristic
shape blueward of 1215\AA\ observed. As we shall see, some of the more
recently discovered objects are close to the galaxy luminosity
function characteristic luminosity $M^{*}$, and some have relatively
weak or maybe even completely absorbed Ly$\alpha$ \citep[e.g. Figures
7 and 10 in][]{Banados2016}. We leave aside detailed investigation and
discussion into espectral features and line strengths, and take as given 
the published spectra.

@@

@@

\subsection{Near-infrared photometry}
Due to their selection of being very faint/undetected in the
observed-frame optical but bright in the observed frame near-infrared,
VH$z$Qs are generally detected in the near-infrared $yYJHK$-bands
\citep[$\approx$0.98-2.38$\mu$m; e.g., ][]{Peth2011}.

@@

%\section{NIR Data}
The near-infrared data in this paper comes from the Wide Field Astronomy Unit's
(WFAU) Science Archives for UKIRT-WFCAM, the WFCAM Science Archive
\citep[WSA][]{WSA} and VISTA-VIRCAM, the VISTA Science Archive
\citep[VSA][]{VSA}. These archives were developed for the VISTA Data Flow System
\citep[VDFS][]{VDFS}.

@@

The data was processed using a forced photometry, or matched-aperture
photometry. A pipeline for this has been developed by WFAU, but
has not yet been incorporated into the main VDFS pipeline. Full details of the
matched-aperture pipeline (MAP) will appear in a forthcoming paper, Cross et al.
2018, in prep, and has also been discussed in \citet{Cross2013} and \citet{Cross2017}.
We will give the pertinent points of the MAP and specific details of these data sets below.

@@

\subsection{Selection of NIR}

@@

\subsection{Setup Matched Aperture Product}

@@

\subsection{Processing MAP data}

A set of apertureIDs were created in \verb+MapApertureIDshighzQsoMap+, based on
the \verb+RequiredMatchedApertureProduct+ {\bf selection} value. This may
seem unnecessary layer since it is a one-to-one match with \verb+finalQsoCatalogue+,
but the layer is a general abstraction that allows multiple sources of
catalogue, and multiple types\ldots
Entries added to \verb+MapSurveyTables+ $\Rightarrow$ not pertinent

\subsubsection{Forced photometry}
CASU's \verb+imcore_list+ was run on each frame assigned to the programme with
the input list equal to objects selected to be within \ldots of the multiframe
centre. In this case, where there are 424 QSOs spread across the sky, there is
typically 1 object per multiframe, but many have two and one,
multiframeID=2614475 in the VSA, has 3 objects. The output of \verb+imcore_list+
is a multi-extension FITS binary table, with identical columns to the CASU FITS
binary tables produced using the CASU \verb+imcore+, the basis of all WFCAM and
VISTA survey products and also familiar to many astronomers through the INTWFS
\citep{}, and VST-ATLAS and -VPHAS \citep{}. Since forced photometry can be run
in many ways on a particular image, a single science frame is not
necessarily linked to a single MAP catalogue, so the \verb+MapFrameStatus+ table
links images ({\bf multiframeID}) to catalogues ({\bf catalogueID}) and gives
information on what processing stage they are at ({\bf bitProcessingFlag}),
whether they have been ingested ({\bf isIngested}), or what quality control has
been run on them ({\bf ppErrBitsStatus}).

@@

\subsubsection{Averaging matched photometry}

Unfortunately the photometry in a single epoch image often has low
signal-to-noise. The advantage of matched aperture photometry on QSOs is that
co-adding is relatively simple: if each epoch is taken in the same aperture
(assuming the astrometry is correct) and the aperture photometry has been
corrected to total: the standard aperture corrections work well for point
sources then averaging the calibrated photometry should give as good as
extracting from a deep stack. In fact it will almost certainly do better, since
the images in some cases are taken from multiple projects with different
pointings. In addition, corrections such as scattered light, pixel distortion
and aperture corrections will be more complex, if not impossible to apply to
deep-stacks but will be automatically applied in the averaging of forced
photometry.

@@

\subsubsection{\ldots}

@@

\iffalse
\subsection{Filter and Survey choices} 
We make some choices when reporting our archival photometry. 
This includes:
\begin{itemize}
\item Report Pan-STARRS1 DR1 $grizy$ wherever we have it; 
\item Report WFCAM $YJHK$ (mainly from the UKIDSS); 
\item Report VIRCAM $YJHK_{\rm S}$ (mainly from the VISTA surveys); 
\item Report VIRCAM $YJH$ over WFCAM  $YJH$; 
\item Report both VIRCAM $K_{\rm S}$ and WFCAM  $K$; 
\item Report DECam $grz$ wherever we have it (mainly from the DES and DECaLS); 
\item Due to lack of coverage, do not report WFCAM $Z$-band. 
\end{itemize}
\fi

@@

    \subsection{Detection Rates in the optical}

@@

@@

    \subsection{Variability}
    Sed elit massa, eleifend non sodales a, commodo ut felis. Sed id
pretium felis. Vestibulum et turpis vitae quam aliquam convallis. Sed
id ligula eu nulla ultrices tempus. Phasellus mattis erat quis metus
dignissim malesuada. Nulla tincidunt quam volutpat nibh facilisis
euismod. Cras vel auctor neque. Nam quis diam risus.

Nunc semper quam et leo interdum vulputate eu quis magna. Sed nec arcu at orci egestas convallis. Aenean quam velit, aliquam vitae viverra in, elementum vel elit. Nunc suscipit aliquet sapien a suscipit. Cras nulla ipsum, posuere eu fringilla sit amet, dapibus ultricies nulla. Nullam eu augue id purus mollis dignissim sed et libero. Phasellus eget justo sed neque pellentesque egestas nec id arcu. Donec facilisis pulvinar sapien et fringilla. Suspendisse vestibulum rhoncus sapien id laoreet. Morbi et orci vitae tortor imperdiet imperdiet. In hac habitasse platea dictumst. Vivamus vel neque id mi ultrices tristique. Integer quam libero, ornare vel gravida in, feugiat a ante. Nam dapibus, tellus vitae pellentesque cursus, dui nisl egestas augue, non fermentum nisl est nec nisi. Vestibulum nec mi justo, eget dapibus velit.

    \subsection{Very High-$z$ Quasars in WISE}
     \citet{Blain2013} 
     Cras in laoreet mauris. Vivamus nec nulla a dui commodo
     adipiscing. Proin vulputate lectus nec arcu iaculis sit amet auctor
     ligula ultricies. Phasellus condimentum gravida tincidunt. Phasellus
     et mauris ac nibh vestibulum vehicula. Morbi et augue id purus gravida
     sagittis quis in sem. Phasellus quis risus bibendum eros luctus
     auctor.

        \subsubsection{Very High-$z$ Quasars Detected in WISE W3 and W4}
        Proin non tempus velit. Etiam laoreet, enim nec scelerisque
        dictum, tortor massa tempor enim, id pretium justo quam ac
        lectus. Maecenas diam nibh, interdum at lobortis sit amet, dignissim
        et quam. Sed tincidunt faucibus risus, congue tempus nisl consectetur
        eget. Suspendisse venenatis turpis ut risus aliquam interdum. In at
        velit sed ligula dictum dignissim ut et dui. Curabitur ac scelerisque
        purus.

@@

This research has made use of the SVO Filter Profile Service
(http://svo2.cab.inta-csic.es/theory/fps/) supported from the Spanish
MINECO through grant AyA2014-55216 
%\citet{} 
The SVO Filter Profile Service\footnote{Rodrigo, C., Solano, E., Bayo, A. http://ivoa.net/documents/Notes/SVOFPS/index.html}
describes the Spanish VO Filter Profile Service. 
The Filter Profile Service Access Protocol. Rodrigo, C., Solano, E. http://ivoa.net/documents/Notes/SVOFPSDAL/index.html

>>>>

\vspace{-16pt}
\section{Data}
In Table~\ref{tab:THE_TABLE} we present our dataset and 
we have assembled this in the following manner.  First
we compile the list of all known, spectroscopically confirmed quasars
from the literature. Most of these objects are easily identified by
their broad Ly$\alpha$ emission line, \nv emission and characteristic
shape blueward of 1215\AA\ observed. As we shall see, some of the more
recently discovered objects are close to the galaxy luminosity
function characteristic luminosity $M^{*}$, and some have relatively
weak or maybe even completely absorbed Ly$\alpha$ \citep[e.g. Figures
7 and 10 in][]{Banados2016}. We leave aside detailed investigation and
discussion into espectral features and line strengths, and take as given 
the published spectra.

@@

We also obtain mid-infrared, $\lambda=3-30\mu$m wavelength data from the
the Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission.
WISE mapped the sky in 4 passbands, in bands centered at wavelengths of 3.4, 4.6, 12, and 23$\mu$m. 
In total the release all sky ``ALLWISE'' catalog, contains nearly 750 million detections at high-significance\footnote{
\href{http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}{http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2\_1.html}}.

@@

\subsection{Near-infrared photometry}~\label{sec:NIR_data} 
Due to their selection of being very faint/undetected in the
observed-frame optical but bright in the observed frame near-infrared,
VH$z$Qs are generally detected in the near-infrared $yYJHK$-bands
\citep[$\approx$0.98-2.38$\mu$m; e.g., ][]{Peth2011}.

@@

The near-infrared data in this paper comes from the Wide Field Astronomy Unit's
(WFAU) Science Archives for UKIRT-WFCAM, the WFCAM Science Archive
\citep[WSA][]{WSA} and VISTA-VIRCAM, the VISTA Science Archive
\citep[VSA][]{VSA}. These archives were developed for the VISTA Data Flow System
\citep[VDFS][]{VDFS}.

@@

The data was processed using a forced photometry, or matched-aperture
photometry. A pipeline for this has been developed by WFAU, but
has not yet been incorporated into the main VDFS pipeline. Full details of the
matched-aperture pipeline (MAP) will appear in a forthcoming paper, Cross et al.
2018, in prep, and has also been discussed in \citet{Cross2013}.  
%% and \citet{Cross2017} -- Can't find Cross et al. 2017 in NASA/ADS.
We will give the pertinent points of the MAP and specific details of these data sets below.

@@

@@

    \subsubsection{Setup Matched Aperture Product}

@@

    \subsubsection{Processing MAP data and Forced photometry} 
    A set of apertureIDs were created in \verb+MapApertureIDshighzQsoMap+, based on
    the \verb+RequiredMatchedApertureProduct+ {\bf selection} value. This may
    seem unnecessary layer since it is a one-to-one match with \verb+finalQsoCatalogue+,
    but the layer is a general abstraction that allows multiple sources of
    catalogue, and multiple types\ldots
    Entries added to \verb+MapSurveyTables+ $\Rightarrow$ not pertinent

    CASU's \verb+imcore_list+ was run on each frame assigned to the programme with
    the input list equal to objects selected to be within \ldots of the multiframe
    centre. In this case, where there are 424 QSOs spread across the sky, there is
    typically 1 object per multiframe, but many have two and one,
    multiframeID=2614475 in the VSA, has 3 objects. The output of \verb+imcore_list+
    is a multi-extension FITS binary table, with identical columns to the CASU FITS
    binary tables produced using the CASU \verb+imcore+, the basis of all WFCAM and
    VISTA survey products and also familiar to many astronomers through the INTWFS, 
    VST-ATLAS and VPHAS.     {\it this needs tidied up, citations added...}
    Since forced photometry can be run
    in many ways on a particular image, a single science frame is not
    necessarily linked to a single MAP catalogue, so the \verb+MapFrameStatus+ table
    links images ({\bf multiframeID}) to catalogues ({\bf catalogueID}) and gives
    information on what processing stage they are at ({\bf bitProcessingFlag}),
    whether they have been ingested ({\bf isIngested}), or what quality control has
    been run on them ({\bf ppErrBitsStatus}).

@@

    \subsubsection{Averaging matched photometry}
    Unfortunately the photometry in a single epoch image often has low
    signal-to-noise. The advantage of matched aperture photometry on QSOs is that
    co-adding is relatively simple: if each epoch is taken in the same aperture
    (assuming the astrometry is correct) and the aperture photometry has been
    corrected to total: the standard aperture corrections work well for point
    sources then averaging the calibrated photometry should give as good as
    extracting from a deep stack. In fact it will almost certainly do better, since
    the images in some cases are taken from multiple projects with different
    pointings. In addition, corrections such as scattered light, pixel distortion
    and aperture corrections will be more complex, if not impossible to apply to
    deep-stacks but will be automatically applied in the averaging of forced
    photometry.

@@

@@

\subsection{MIR data}
The MIR data for this study comes exclusively from the Wide-field
Infrared Survey Explorer (WISE) mission. Since we are only concerned
here with the very large area ($\gg1000$ deg$^2$) surveys, we leave
exploration of the VH$z$Q population in e.g. the large Spitzer areal
surveys such as the Spitzer IRAC Equatorial Survey \citep[SpIES;
][]{Timlin2016}, the Spitzer-HETDEX Exploratory Large-area Survey
\citep[SHELA; ][]{Papovich2016} and the Spitzer-SPT Deep Field
\citep[SSDF; ][]{Ashby2013}, to a future investigation. This will also
include a detailed study of MIR spectra e.g. \citet{Lambrides2018}.

We use data from the the beginning of the WISE mission \citep[2010
January; ][]{Wright2010} through the fourth-year of NEOWISE-R
operations \citep[2017 December;]{Mainzer2011}. More specifically, we
use the data from the
\href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE}
program and catalogue, which combines data from the WISE cryogenic and
NEOWISE (Mainzer et al. 2011 ApJ, 731, 53) post-cryogenic survey
phases. For the our variability investigations, we supplement the
ALLWISE data with data from the
\href{http://wise2.ipac.caltech.edu/docs/release/neowise/neowise_2018_release_intro.html}{NEOWISE
2018 Data Release}. NEOWISE 2018 makes available the 3.4 and 4.6 μm
(W1 and W2) single-exposure images and extracted source information
that were acquired between 2016 December 13 and 2017 December 13 UTC,
which was the fourth year of survey operations of the Near-Earth
Object Wide-field Infrared Survey Explorer Reactivation Mission
(NEOWISE; Mainzer et al. 2014, ApJ, 792, 30). The fourth year NEOWISE
data products are concatenated with those from the first three years
(originally released on March 26, 2015, March 23, 2016 and June 1,
2017) into a single archive.

The WISE scan pattern leads to coverage of the full- sky approximately
once every six months (a``sky pass''), but the satellite was placed in
hibernation in 2011 February and then reactivated in 2013
October. Hence, our light curves have a cadence of 6 months with a 32
month sampling gap.

@@

    %\subsection{Detection Rates in the optical}

@@

    \citet{Blain2013} Cras in laoreet mauris. Vivamus nec nulla a dui
    commodo adipiscing. Proin vulputate lectus nec arcu iaculis sit amet
    auctor ligula ultricies. Phasellus condimentum gravida
    tincidunt. Phasellus et mauris ac nibh vestibulum vehicula. Morbi et
    augue id purus gravida sagittis quis in sem. Phasellus quis risus
    bibendum eros luctus auctor.

@@

    %\subsubsection{
    Very High-$z$ Quasars Detected in WISE W3 and W4.
    Proin non tempus velit. Etiam laoreet, enim nec scelerisque
    dictum, tortor massa tempor enim, id pretium justo quam ac
    lectus. Maecenas diam nibh, interdum at lobortis sit amet, dignissim
    et quam. Sed tincidunt faucibus risus, congue tempus nisl consectetur
    eget. Suspendisse venenatis turpis ut risus aliquam interdum. In at
    velit sed ligula dictum dignissim ut et dui. Curabitur ac scelerisque
    purus.

\begin{figure}
   \centering
   \includegraphics[width=8.5cm]
   {/cos_pc19a_npr/programs/quasars/highest_z/MIR_LCs/NEOWISER_LC_histogramlog_20180827.png}
   \vspace{-16pt}
   \caption[]
   {Histogram showing the number of NEOWISE-R epochs and detections there are for each 
    VH$z$Q.} 
   \label{fig:MIR_LC_epochs}
 \end{figure}

\subsection{Variability}
VH$z$Qs, if accreting at, or above the Eddington Limit, might well
have have large values of changing mass accretion rate, $\ddot{m_{\rm
    accr}}$. A consequence of this would be that these quasar exhibit
signs of variability, most likely showing up in their UV/optical
rest-frame spectra. We look for evidence of this variability signature
in the NIR and MIR light-curves of the VH$z$Qs. As a guide, \civ
enters the $Y$-band at redshift $z$=5.32 and exits at $z$=5.99, and
enters the $J$-band at redshift $z=6.55$ and exits at $z$=7.57. \mgii
enters the $H$-band at redshift $z=4.33$ and exits at $z=5.37$ and
enters the $K$-band at redshift $z=6.25$ and exits at $7.50$.

    Using the extended datasets described in Section~\ref{sec:NIR_data} and~\ref{sec:NIR_SQL}, we unc semper quam et leo interdum vulputate eu quis magna. Sed nec arcu at orci egestas convallis. Aenean quam velit, aliquam vitae viverra in, elementum vel elit. Nunc suscipit aliquet sapien a suscipit. Cras nulla ipsum, posuere eu fringilla sit amet, dapibus ultricies nulla. Nullam eu augue id purus mollis dignissim sed et libero. Phasellus eget justo sed neque pellentesque egestas nec id arcu. Donec facilisis pulvinar sapien et fringilla. Suspendisse vestibulum rhoncus sapien id laoreet. Morbi et orci vitae tortor imperdiet imperdiet. In hac habitasse platea dictumst. Vivamus vel neque id mi ultrices tristique. Integer quam libero, ornare vel gravida in, feugiat a ante. Nam dapibus, tellus vitae pellentesque cursus, dui nisl egestas augue, non fermentum nisl est nec nisi. Vestibulum nec mi justo, eget dapibus velit.

\begin{figure}
   \includegraphics[width=8.5cm]
   {/cos_pc19a_npr/programs/quasars/highest_z/MIR_LCs/three_MIR_LC_egs_20180827.pdf}
   \centering
   \caption[]
   {Here we show the MIR NEOWISE-R for J0100+2802 \citep{Wu2015}, J0224-4711 and  J1626+2751. 
     Red points are the W1 band; cyan points the W2 band.} 
   \label{fig::MIR_LC_3egs}
 \end{figure}

    Figure~\ref{fig:MIR_LC_epochs} gives the number of NEOWISE-R epochs and detections there are for each VH$z$Q, while 
Figure~\ref{fig:MIR_LC_3egs} presents three examples of the MIR lighcurves and associated colour changes. Here we show 
J0100+2802 \citep{Wu2015}, J0224-4711 and  J1626+2751.

@@

This research has made use of the SVO Filter Profile Service
(http://svo2.cab.inta-csic.es/theory/fps/) supported from the Spanish
MINECO through grant AyA2014-55216 
%%
The SVO Filter Profile Service\footnote{Rodrigo, C., Solano, E., Bayo, A. http://ivoa.net/documents/Notes/SVOFPS/index.html}
describes the Spanish VO Filter Profile Service. 
The Filter Profile Service Access Protocol. Rodrigo, C., Solano, E. http://ivoa.net/documents/Notes/SVOFPSDAL/index.html
